\documentclass{beamer}	% Compile at least twice!
%\setbeamertemplate{navigation symbols}{}
\usetheme{Warsaw}
%\useinnertheme{rectangles}
%\useoutertheme{infolines}
\useoutertheme[title,section,subsection=true]{smoothbars}
 
% -------------------
% Packages
% -------------------
\usepackage{
	amsmath,			% Math Environments
	amssymb,			% Extended Symbols
	enumerate,		    % Enumerate Environments
	graphicx,			% Include Images
	lastpage,			% Reference Lastpage
	multicol,			% Use Multi-columns
	multirow,			% Use Multi-rows
	pifont,			    % For Checkmarks
	stmaryrd			% For brackets
}
\usepackage[english]{babel}
\usepackage[UTF8]{ctex}

% -------------------
% Colors
% -------------------
\definecolor{UniOrange}{RGB}{212,69,0}
\definecolor{UniGray}{RGB}{62,61,60}
%\definecolor{UniRed}{HTML}{B31B1B}
%\definecolor{UniGray}{HTML}{222222}
\setbeamercolor{title}{fg=UniGray}
\setbeamercolor{frametitle}{fg=UniOrange}
\setbeamercolor{structure}{fg=UniOrange}
\setbeamercolor{section in head/foot}{bg=UniGray}
\setbeamercolor{author in head/foot}{bg=UniGray}
\setbeamercolor{date in head/foot}{fg=UniGray}
\setbeamercolor{structure}{fg=UniOrange}
\setbeamercolor{local structure}{fg=black}
\beamersetuncovermixins{\opaqueness<1>{0}}{\opaqueness<2->{15}}


% -------------------
% Fonts & Layout
% -------------------
\useinnertheme{default}
\usefonttheme{serif}
\usepackage{palatino}
\setbeamerfont{title like}{shape=\scshape}
\setbeamerfont{frametitle}{shape=\scshape}
\setbeamertemplate{itemize items}[circle]
%\setbeamertemplate{enumerate items}[default]


% -------------------
% Commands
% -------------------

% Special Characters
\newcommand{\N}{\mathbb{N}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\C}{\mathbb{C}}

% Math Operators
\DeclareMathOperator{\im}{im}
\DeclareMathOperator{\Span}{span}

% Special Commands
\newcommand{\pf}{\noindent\emph{Proof. }}
\newcommand{\ds}{\displaystyle}
\newcommand{\defeq}{\stackrel{\text{def}}{=}}
\newcommand{\ov}[1]{\overline{#1}}
\newcommand{\ma}[1]{\stackrel{#1}{\longrightarrow}}
\newcommand{\twomatrix}[4]{\begin{pmatrix} #1 & #2 \\ #3 & #4 \end{pmatrix}}


% -------------------
% Tikz & PGF
% -------------------
\usepackage{tikz}
\usepackage{tikz-cd}
\usetikzlibrary{
	calc,
	decorations.pathmorphing,
	matrix,arrows,
	positioning,
	shapes.geometric
}
\usepackage{pgfplots}
\pgfplotsset{compat=newest}


% -------------------
% Theorem Environments
% -------------------
\theoremstyle{plain}
\newtheorem{thm}{Theorem}[section]
\newtheorem{prop}{Proposition}[section]
\newtheorem{lem}{Lemma}[section]
\newtheorem{cor}{Corollary}[section]
\theoremstyle{definition}
\newtheorem{ex}{Example}[section]
\newtheorem{se}{Section}[section]
\newtheorem{nex}{Non-Example}[section]
\newtheorem{dfn}{Definition}[section]
\theoremstyle{remark}
\newtheorem{rem}{Remark}[section] 
\numberwithin{equation}{section}


% -------------------
% Title Page
% -------------------
\title{\textcolor{white}{SurviveWUSTManual}}
% \subtitle{\textcolor{white}{Mathematics Conference for the Mysterious and Magical}}  
\author{Project Team}
\date{\time} 


% -------------------
% Content
% -------------------
\begin{document}


% Title Page
\begin{frame}
\titlepage
\end{frame}



% Motivation
\section{序}



% My Motivation 
\begin{frame}

	\begin{se}
		序
	\end{se}

	Survive-WUST-Manual（武汉科技大学求生手册）项目灵感来自于Survive-SJTU-Manual（上海交通大学求生手册），旨在帮助初入校园的同学更快地适应大学生活，完成从高中生到大学生的身份转变。

在Survive-WUST-Manual中，我们将多维度探讨大学生活的可能性，辅助读者的价值判断与生涯规划。
	

\end{frame}

\begin{frame}
	\begin{se}
		手册说明
	\end{se}
	\textbf{武汉科技大学生存手册}
	由一群武科大本科生（计算机学院学生为主）写就，手册写作灵感来自于上海交通大学生存手册。
	\vspace{\baselineskip}
	
	本手册与上交大版本不同之处在于，本手册是依据武汉科技大学真实情况写就的，对原版本中的许多内容进行了适用性修改。

	\vspace{\baselineskip}
	由于项目团队成员暂主要为大一大二的本科生，本手册在以下内容板块可能存在欠缺——
	\begin{enumerate}
		\item 国内深造
		\item 出国留学
		\item 科研道路
	\end{enumerate}

\end{frame}

\begin{frame}
	欢迎在邮件中提 issue 以向我们提供反馈建议，我们乐于采纳您的建议！
	
	\vspace{\baselineskip}
	
	本项目通过 Gitbook 发布，我们将长期维护此项目（维护周期可能数年），希望给未来的武科大在读和入学新生同学带来微小的帮助，尤其感谢手册的初代作者们！
\end{frame}

% Definitions & Examples
\begin{frame}

	\begin{se}
	
	\end{se}

\begin{dfn}[Ph.D.]


\end{dfn}

\begin{ex}
I studied so hard for my qualifying exam I replaced my childhood memories with an entire chapter of Hartshorne's \emph{Algebraic Geometry}.
\end{ex}
\end{frame}



% Main Results
\section{立志篇}



% Theorem
\begin{frame}
\begin{thm}[D.]
For all $n$, we have $n^2= n \cdot n$.
\end{thm}

\pf With massive loss of generality, let $n=1$. Then we have
	\[
	1=1^2= 1 \cdot 1= 1
	\]
Therefore by overwhelming hope, it must always be true. \qed
\end{frame}



% Corollary
\begin{frame}
Most algebra you need to be true is true.
\begin{cor}
For all $n,m \in \N$, $(n+m)^2= n^2 + m^2$.
\end{cor}
\end{frame}



% Applications
\section{访谈篇}



% Application 1
\begin{frame}
	\begin{enumerate}[1.]
	\item Bleach is mostly water. \pause
	\item We are mostly water. \pause
	\item Therefore, we are bleach.
	\end{enumerate} \vspace{0.5cm}

Now we pause for the big reveal\dots \pause \vspace{0.3cm}

	\begin{itemize}
	\item I am clearly a master of logic.
	\item Masters of logic get Ph.D's.
	\item I have earned this.
	\end{itemize}
\end{frame}



% Math
\begin{frame}
Finally! Some Math! \vspace{1cm}

Here is some Math: $\int_1^\alpha \dfrac{x^2}{\sin x^2} \;dx$ and $\sum i^2$. \vspace{1cm}

But you could make this Math big inline with `displaystyle': $\ds \int_1^\alpha \dfrac{x^2}{\sin x^2} \;dx$ and $\ds \sum i^2$. \vspace{1cm}

And even more Math:
	\[
	\oint \vec{\nabla} \times \vec{F} \;dV = \sum_{n=1}^\infty \ov{p} \twomatrix{a}{b}{c}{d}
	\]
\end{frame}



% Conclusion
\section{生存技巧}



% End Slide
\begin{frame}
Ph.D. plz\dots
\end{frame}



% Questions
\begin{frame}
\begin{center} {\bfseries \Large Questions?} \end{center}
\end{frame}

\end{document}